Key Derivation From Noisy Sources With More Errors Than Entropy

### 2014-02-08 trunk/constantRate/ConstCompFuzzExt.tex

Both constructions are based on  obfuscation of point programs~\cite{canetti1997towards}.  A point program $I_w(x)$ outputs $1$ if $x=w$ and $0$ otherwise.  Intuitively, an obfuscated version of a program reveals nothing past its input and output behavior.  For a point program, this means hiding all partial information about the point $w$.
We need a strong version of point obfuscation that remains secure even when several obfuscations of correlated points are composed. While the standard definition of obfuscation \cite{barak2001possibility} does not imply security under composition, we can base our construction on the relaxed notion of \emph{virtual grey-box} obfuscation introduced in~\cite{bitansky2010strong}. For this notion, \cite{bitansky2010strong} construct composable obfuscation of point programs under particular number-theoretic assumptions. Additionally, such obfuscation can be made very efficient under a strong assumption on cryptographic hash functions~\cite{canetti1997towards}. We note that the problem of fuzzy extractors remains non-trivial even given the recent progress on general purpose obfuscation \cite{GargGH0SW13,BrakerskiR13,BarakGKPS13}, as the achieved notions of obfuscation seem to be insufficient.

We note that the problem of fuzzy extractors remains non-trivial even given the recent construction of general purpose indistinguishably obfuscation \cite{GargGH0SW13,PST13}, as the weaker notion of indistinguishably obfuscation seems insufficient for our application.\bnote{this sentence needs to be cleaned up} \bnote{what is PST?}

>>>>

Both constructions are based on  obfuscation of point programs~\cite{canetti1997towards}.  A point program $I_w(x)$ outputs $1$ if $x=w$ and $0$ otherwise.  Intuitively, an obfuscated version of a program reveals nothing past its input and output behavior.  For a point program, this means hiding all partial information about the point $w$.
We need a strong version of point obfuscation that remains secure even when several obfuscations of correlated points are composed. While the standard definition of obfuscation \cite{barak2001possibility} does not imply security under composition, we can base our construction on the relaxed notion of \emph{virtual grey-box} obfuscation introduced in~\cite{bitansky2010strong}. For this notion, \cite{bitansky2010strong} construct composable obfuscation of point programs under particular number-theoretic assumptions. Additionally, such obfuscation can be made very efficient under a strong assumption on cryptographic hash functions~\cite{canetti1997towards}.

We note that fuzzy extractors for the setting where $\Huse\le 0$ can be trivially constructed from a strong form of obfuscation, specifically, virtual black-box obfuscation for the class {\em proximity point programs}, $I_w(x)$ that tests if $x$ is within distance $t$ of $w$. However, currently we do not know if such obfuscation exists. Recent works constructed candidates indistinguishability obfuscators \cite{GargGH0SW13,PassTS13} and virtual black-box obfuscators in idealized model \cite{BrakerskiR13,BarakGKPS13} for all programs. However, these notions of obfuscation do not imply virtual-black-box obfuscation for proximity point programs in the plain model. The work of \cite{BarakBCKPS13} suggest an average-case virtual-black-box obfuscator for the family of {\em evasive} functions that test if a low-degree multi-variant arithmetic circuit evaluates to zero. However, we do not know if these functions include proximity point programs.
